---
title: "Regression Models Peer Graded Assignment"
author: "K Ajay Rangan"
date: "03/11/2020"
output: pdf_document
---
```{r}
library("plyr")
```

## Automatic vs Manual Transmission for better Mileage

### Instructions
You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

“Is an automatic or manual transmission better for MPG”
"Quantify the MPG difference between automatic and manual transmissions"

## Dataset 

Import the dataset
```{r}
data(mtcars)
head(mtcars)
```
In the dataset the am column shows what type of transmission the car has.
According to the Documentation:
[, 9]	am	Transmission (0 = automatic, 1 = manual)
We require only the mpg and the am column for our analysis. 
Lets create a dataframe with only these variables.

```{r}
mydata <- mtcars[c("mpg","am")]
head(mydata)
```

## Exploratory Analysis

```{r}
summary(mydata)
```

```{r}
boxplot(mpg~am, data = mydata)
```

A very preliminary Analysis shows the superiority of Manual Transmission in Mileage.

Lets create some models to find out, but lets also keep in mind, there may be other variables that affect this. 
The results of the difference in mpg aren't solely due to the type of transmission. 

```{r}
count(mtcars, vars = "am")
```
There are slightly more Automatic than Manual cars in this dataset

## Model

```{r}
premodel <- lm(mpg ~ ., mtcars);
summary(premodel)
```

From the table we can note that wt, am, drat, qsec, gear have high coefficients and are significant in our model

Lets compare multiple models using ANOVA

```{r}
anova(lm(mpg ~ am, mtcars),                           
      lm(mpg ~ am + wt, mtcars),                      
      lm(mpg ~ am + wt + qsec, mtcars),               
      lm(mpg ~ am + wt + qsec + drat, mtcars),        
      lm(mpg ~ am + wt + qsec + drat + gear, mtcars)
      )     
```

We see high P values for the 4th and 5th Model. 
The 3rd model seems to be a better one given lower RSS and P.
This includes am, wt and qsec.

```{r}
model2 <- lm(mpg ~ am + wt + qsec, mtcars)
par(mfrow = c(2,2)); plot(model2)
```

```{r}
model1 <- lm(mpg~am,mtcars)
coef(model1)
coef(model2)
```

## Executive Summary
As we can see in general Manual cars have a mileage about 7.244939 higher than automatic transmission. 
If we bring in other variables like wt and qsec which are significant into the picture, Manual cars have higher mileage by about 2.935837.

In either case its safe to say Manual cars have a better mileage.